Dynamic Walking and Whole-Body Motion Planning for Humanoid Robots: an Integrated Approach

### 2012-12-04 stc1.tex
Increase small-space figure size and add balls labels.

\definecolor{cc6c6c6}{RGB}{198,198,198}
\definecolor{cffffff}{RGB}{255,255,255}

\begin{tikzpicture}[y=0.4pt, x=0.4pt,yscale=-1, inner sep=0pt, outer sep=0pt]
% path5273
\path[shift={(-0.42857142,4.7142857)},draw=black,miter limit=4.00,line
  width=0.800pt]
  (365.7143,269.5050)arc(0:180:97)arc(-180:0:97) --
  cycle;

@@

@@

>>>>

\definecolor{cc6c6c6}{RGB}{198,198,198}
\definecolor{cffffff}{RGB}{255,255,255}
\definecolor{darkGrey}{RGB}{75,75,75}

\begin{tikzpicture}[y=0.7pt, x=0.7pt,yscale=-1, inner sep=0pt, outer sep=0pt]
% path5273
\path[shift={(-0.42857142,4.7142857)},draw=black,miter limit=4.00,line
  width=0.800pt]
  (365.7143,269.5050)arc(0:180:97)arc(-180:0:97) --
  cycle;

@@

% Ball epsilon q
\path[fill=black] (330,200) node[above right] (text2834) {$\mathcal{B}_{\epsilon}(q)$};

@@

% Ball eta q
\path[fill=black] (320,258) node[above right, color=darkGrey] (text2838) {$\mathcal{B}_{\eta}(q)$};
